### 2018-10-18 Sections/cryptowars.tex
Some quotes
Editing on QKD attacks section

@@

@@

For a QKD system, information-theoretic security is achieved only when security against collective, coherent attacks is proven. Hacking attacks are related to the weaknesses of the physical  implementation, rather than weakness of the theory. Some examples of weaknesses which allow zero-error attacks include losses and imperfect components. When considering the security of noisy channels, one must assume that all noise is due to manipulation by an eavesdropper. An attack attempt is considered successful if it can be proven that the eavesdropper can gain a non-negligible (i.e., not exponentially small) amount of informationon the final secret key extracted by Alice and bob without alerting them. Some of the well-known attacks follows.

\subsection{Trojan horse attack}
The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by
sending light into their devices and collecting the reflected signal. 
The first one of this kind of attacks actually came for free for the eavesdropper \cite{}: it was discovered that some photon counters emits light when a photon was detected \cite{}. If the emitted light carries information on which detector was triggered, it must be prevented to leak out.

\subsection{Beam-splitter and photon number splitting attack}

Ref.~\cite{PhysRevLett.68.3121}

A beam-splitting (BS) attack translates the fact that any signal lost in channel is stolen by Eve. Here Eve induces losses in the communication channel by putting a beam splitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels and does not introduce any error.

If the state preparation consists of more than one photon, Eve can count the number of photons in each signal and act accordingly. Such attacks are called photon-number splitting (PNS) attacks. The BS and PNS attacks were discovered as zero-error attacks against BB84 implemented with a weak laser pulses. To counter the attack, the decoy-state method\cite{} method was developed.

\subsection{Attacks on the detector}
The Faked-state attack is based on the weak-laser implementation of BB84. Here Eve manipulates Bob's detectors to force him to measure in the same basis. It exploits the fact that the detectors may have a dead time, and the eavesdropper can trigger the detector when she wants to. 
It follows that Bob's detection outcomes is controlled by the eavesdroper.

Eve can also go behond detector blinding. She can send in a powerful laser pulse to optically damage component in the QKD system and permanently change its characteristics\cite{}. If the new characteristics then assist the eavesdropper in an attack without Alice or Bob being notified, the security of that practical QKD system would be severly compromised.
% 
% 
A more detailed discussion on attacks on the physical implementation can be found in Ref.~\cite{}.

>>>>

\famousquote{I would rather have questions that can't be answered than answers that can't be questioned.}{Richard Feynman}
\newline

@@

%
% Attacks on QKD
%

@@

\dropcap{F}{or} a QKD system, information-theoretic security\index{Information-theoretic security} is achieved only when security against collective, coherent attacks is proven. We mustn't make assumptions about the limitations of our adversaries. Hacking attacks are related to the weaknesses of the physical implementation, rather than weakness of the theory. Some examples of weaknesses which allow zero-error attacks include losses, imperfect components, or correlations between signals leaking information.

When considering the security of noisy channels, one must assume that all noise is due to manipulation by an eavesdropper, the worst-case scenario. An attempted attack is considered successful if it can be proven that the eavesdropper can gain a non-negligible (i.e not exponentially small) amount of mutual information with the final secret-key established between Alice and Bob, without alerting them. Some of the well-known attacks follow.

\subsection{Trojan horse attack}\index{Trojan horse attacks}

The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by sending light into their devices and collecting the reflected signal. The first one of this kind of attacks actually came for free for the eavesdropper \cite{bib:RevModPhys.81.1301}: it was discovered that some photon-counters emit light when a photon is detected \cite{bib:kurtsiefer2001breakdown}. If the emitted light carries correlated information on which detector was triggered, it must be prevented from leaking outside the secure space and becoming accessible to Eve.

\subsection{Beamsplitter and photon-number-splitting attacks}\index{Beamsplitter attacks}\index{Photon-number-splitting attacks}

A beamsplitting (BS) attack translates the fact that any signal lost over a channel is acquired by Eve. Here Eve induces losses in the communication channel by putting a beamsplitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels, and does not introduce any errors.

If the state preparation consists of more than one photon, Eve can count the number of photons in each signal and act accordingly. Such attacks are called photon-number-splitting (PNS) attacks \cite{bib:PhysRevLett.68.3121}. The BS and PNS attacks were discovered as zero-error attacks against BB84 implemented with weak laser pulses. To counter the attack, the decoy-state\index{Decoy states} method \cite{bib:PhysRevLett.91.057901, bib:PhysRevLett.94.230504} was developed.

\subsection{Detector attacks}\index{Detector attacks}

The faked-state attack\index{Faked-state attack} is based on the weak-laser implementation of BB84. Here Eve manipulates Bob's detectors to force him to measure in the same basis. It exploits the fact that the detectors may have a dead-time\index{Dead-time}, and the eavesdropper can trigger the detector whenever she chooses. It follows that Bob's detection outcomes are controlled by the eavesdropper.

Eve can also go beyond detector blinding. She can send in a powerful laser pulse to optically damage components in the QKD system and permanently change its characteristics \cite{bib:jain2016attacks}. If the new characteristics then assist the eavesdropper in an attack without Alice or Bob being notified, the security of the QKD system would be severely compromised.

A more detailed discussion on attacks on physical implementation can be found in \cite{bib:jain2016attacks}.

### 2018-10-18 Sections/economics_of_the_quantum_internet.tex
Editing on QKD attacks section

Building upon some of the pricing models introduced earlier in this section, there are two main candidates for backing a cryptocurrency with quantum compute-time: the spot market\index{Spot market} (i.e we execute the computation immediately); and the futures market\index{Futures market} (i.e we own the right to utilise the computer at some fixed time in the future). We consider the merits of both these candidates.

@@

The described protocol, in addition to mining a new coin, associated with the execution of a computation, acts as a currency converter for converting traditional assets (e.g dollars) into QuantCoins\texttrademark. This ability to currency convert is necessary, and completely differs from the original Bitcoin mining process, where coins are fabricated out of thin air by anyone and everyone, independent of their pre-existing monetary wealth -- Bitcoins are not created via conversion from any existing asset. The fact that the computation associated with each QuantCoin\texttrademark\, is of intrinsic value on the other hand, implies that Alice ought to be paying something for the service.

@@

The main security risk is that of Bob taking Alice's dollars and running, upon receiving the upfront reward in dollars, which necessarily don't reside on the Blockchain since they are not crypto-assets. This could be addressed by introducing trusted third-party escrow agents into the protocol.

However, if the upfront payment were being made in pre-existing QuantCoins\texttrademark\,, the Blockchain might be programmed to not release the reward until completion of the final verification stage of the protocol -- effectively an escrow programmed directly into the Blockchain for self-execution.

@@

We leave explicit construction of a futures-based QuantCoin\texttrademark\, model as an exercise for the interested reader.

@@

Elasticity of demand is just one context where the concept of elasticity can be applied. Other contexts include: the elasticity of supply, measuring the supply side responsiveness to changes in price; income elasticity, which captures how the quantity of goods in the market change relative to changes in the income of consumers; and cross-price elasticity which compares the percentage change in quantity of one good, relative to the percentage change in price of another good. An example that we will come back to is how changes in the price of quantum computing may have an effect on the quantity demanded of high-performance classical computing (i.e conventional supercomputing).

@@

A number of factors will affect the elasticity of demand and supply in the qubit market. The most significant factor affecting the demand for qubits is the availability of substitutes\index{Substitution}. Given that quantum processing can efficiently solve unique problems that classical computing cannot, there are no close substitutes for qubits -- a transistor is no substitute for a qubit! Consequently, elasticity of demand will be relatively inelastic: the quantity of qubits demanded will be relatively unresponsive to price fluctuations and changes.

The supply side of the equation is also initially going to be highly inelastic. However, as time progresses and technological advancements and enhancements increase the computational power of the quantum internet, the supply of qubits will become increasingly responsive to price fluctuations \comment{Why?}. However, the extent to how elastic the supply becomes over time is also going to be affected by potential for excess capacity given the exponential trajectory of the manufacture of qubits as new and improved fabrication technologies emerge.

@@

We now consider the effect of taxation on quantum resources, specifically in the form of a \textit{qubit tax} -- a sales tax on the purchase of physical qubits. Although this model of taxation is unlikely to be implemented as we describe, it serves as an insightful test-bed for thought experiments into the qualitative implications of taxing quantum assets.

Imagine that consumers have an amount of capital available for the purchase of qubits. Let $\gamma_T$ be the rate of taxation (\mbox{$\gamma_T=1$} represents no taxation, \mbox{$\gamma_T>1$} represents positive taxation, and \mbox{$\gamma_T<1$} represents subsidisation). Then the cost of physical qubits is marked up by $\gamma_T$, reducing the number of qubits that can be afforded by the consumers to,
\begin{align}
	N_\mathrm{tax} = \frac{N_\mathrm{no\,tax}}{\gamma_T}.
\end{align}

@@

This demonstrates that the computational power of classical networks is simply inversely proportional to the rate of taxation, i.e a linear tax performance multiplier, as we intuitively expect. And for quadratic scaling functions the dependence is inverse quadratic in the taxation rate. In both cases the multiplier is a constant factor, independent of the network size. However, for exponential scaling functions we observe an exponential dependence on both the rate of taxation and the size of the network, shown in Fig.~\ref{fig:tax_exp}(left). Note that for large networks executing computations with exponential scaling functions, there is enormous sensitivity to variations in tax rates, yielding very high leverage in computational return by tax rates.

@@

However, taxation could also be negative, in the form of subsidisation. In Fig.~\ref{fig:tax_exp}(right) we focus on the region surrounding neutral taxation, showing small degrees of taxation and subsidisation on either side. Evidently, even small degrees of subsidisation have a very strong effect on the performance multiplier (more pronounced than the same rate of positive taxation!). This makes subsidisation of qubit expansion highly tempting.

@@

An important implication of the imposition of the tax is the share of the taxation burden\index{Taxation}. The change in price from the efficient price, $P_e$, to the new market price faced by consumers, $P_c$, is somewhat equivalent to the shift from $P_e$ to the price point that the suppliers of qubits will receive, $P_s$. This means that the tax burden is likely to be equally shared between producers and consumers, which in the long term could act as a disincentive to increased production.

@@

This will give rise to a marketplace for tradable units of quantum computation, where the underlying asset is time-shares in the global network. We refer to this as the \textit{quantum stock market} -- a marketplace subject to ordinary supply and demand, economic, and psychological pressures. In a scenario where a large number of users are executing computations with high return (think the R\&D lab), asset values will be traded up. Contrarily, in a scenario of low-return computations (think our poor undergrad), they will be traded down. These market forces will be highly time-dependent, varying against many other factors in the economy, such as the emergence of new applications for quantum computation -- the discovery of an important new algorithm could spontaneously distort the market.

@@

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stock market, betting on changes in demand for computation and their associated subjective cost. This trading could involve transactions in the direct underlying asset, future contracts (Sec.~\ref{sec:for_contr}) for locking in required computational power at future points in time, or more complex derivatives. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their return on investment\index{Return on investment (RoI)} will reflect these market dynamics.

As all markets for tradable assets do, sophisticated derivative markets will inevitably emerge, whereby people can speculate on or hedge against market dynamics, taking long, short, or more complex market positions, potentially in a highly-leveraged manner. As discussed in Sec.~\ref{sec:for_contr}, derivatives such as future contracts can be extremely helpful in enabling consumers to lock in future prices, creating a stable business climate. Similarly, other derivatives will enable market participants to hedge\index{Hedging} other quantum-related investments. For example, suppose an investor held a stake in an R\&D lab, highly reliant on quantum computing resources. By taking a leveraged long position on the market value for computation, he may limit losses on his R\&D investment associated with the higher price (and hence lower profit) they will be paying for computation. No doubt, market manipulation and all the usual nonsense and shenanigans will ensue.

@@

\captionspacetab \caption{Summary of the dynamics of various economic models under several computational scaling functions ($f_\mathrm{sc}$) of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\mathrm{global}=\sum_{j\in \mathrm{nodes}} n_j$} qubits in the global network. $N_0$ is the initial number of qubits, undergoing growth rate $\gamma_N$. $C_0$ is the initial monetary cost per qubit, undergoing decay rate $\gamma_C$. $\gamma_\mathrm{ror}$ is the rate of return on the licensing of compute-time on qubits, and $r_\mathrm{rf}$ is the risk-free rate of return. $\gamma_T$ is the rate of taxation, and $N_\mathrm{tax}$ is the number of qubits that would exist on the network in the absence of taxation.} \label{tab:summary_ec_models}

>>>>

Building upon some of the pricing models introduced earlier in this section, there are two main candidates for backing a cryptocurrency with quantum compute-time:
\begin{itemize}
	\item Spot market\index{Spot market}: we execute the computation immediately in exchange for a coin.
	\item Futures market\index{Futures market}: we own the right to utilise the computer at some fixed time in the future in exchange for a coin.
\end{itemize}
We consider the merits of both these candidates.

@@

The described protocol, in addition to mining a new coin, associated with the execution of a computation, acts as a currency converter for converting traditional assets (e.g dollars) into QuantCoins\texttrademark. This ability to currency convert is necessary, and completely differs from the original Bitcoin mining process, where coins are fabricated out of thin air by anyone and everyone, independent of their pre-existing monetary wealth -- Bitcoins are not created via conversion from any existing asset, they are an entirely new asset class of their own. The fact that the computation associated with each QuantCoin\texttrademark\, is of intrinsic value on the other hand, implies that Alice ought to be paying something for the service.

@@

The main security risk is that of Bob taking Alice's dollars and running, upon receiving the upfront reward in dollars, which necessarily don't reside on the Blockchain since they are not crypto-assets. This could be addressed by introducing trusted third-party escrow agents into the protocol, as method currently used in some online dark markets\index{Dark markets}.

However, if the upfront payment were being made in pre-existing QuantCoins\texttrademark\,, the Blockchain might be programmed to not release the reward until completion of the final verification stage of the protocol -- effectively an escrow programmed directly into the Blockchain for self-execution. Such self-executing smart-contracts are already a feature in some cryptocurrencies such as Ethereum\index{Ethereum}.

@@

We leave explicit construction of a futures-based QuantCoin\texttrademark\, model as an exercise for the interested reader, primarily because we haven't thought it through properly\index{Laziness}.

@@

Elasticity of demand is just one context where the concept of elasticity can be applied. Other contexts include: the elasticity of supply, measuring the supply side responsiveness to changes in price; income elasticity, which captures how the quantity of goods in the market change relative to changes in the income of consumers; and cross-price elasticity, which compares the percentage change in quantity of one good, relative to the percentage change in price of another good. An example that we will come back to is how changes in the price of quantum computing may have an effect on the quantity demanded of high-performance classical computing (i.e conventional supercomputing).

@@

A number of factors will affect the elasticity of demand and supply in the qubit market. The most significant factor affecting the demand for qubits is the availability of substitutes\index{Substitution}. Given that quantum processing can efficiently solve unique problems that classical computing cannot, there are no close substitutes for qubits -- a transistor is no substitute for a qubit! Consequently, elasticity of demand will be relatively inelastic: the quantity of qubits demanded will be relatively unresponsive to price fluctuations and changes, since there are no viable alternatives to substitute with.

The supply side of the equation is also initially going to be highly inelastic. However, as time progresses and technological advancements and enhancements increase the computational power of the quantum internet, the supply of qubits will become increasingly responsive to price fluctuations \comment{Why?}. However, the extent to how elastic the supply becomes over time is also going to be affected by potential for excess capacity given the exponential trajectory of the manufacture of qubits as new and improved fabrication technologies emerge -- the quantum Moore's Law\index{Quantum Moore's Law}.

@@

We now consider the effect of taxation on quantum resources, specifically in the form of a \textit{qubit tax}\index{Qubit tax} -- a sales tax on the purchase of physical qubits. Although this model of taxation is unlikely to be implemented as we describe, it serves as an insightful test-bed for thought experiments into the qualitative implications of taxing quantum assets.

Imagine that consumers have an amount of capital available for the purchase of qubits. Let $\gamma_T$ be the rate of taxation (\mbox{$\gamma_T=1$} represents no taxation, \mbox{$\gamma_T>1$} represents positive taxation, and \mbox{$\gamma_T<1$} represents subsidisation). Then the cost of physical qubits is marked up by $\gamma_T$, reducing the number of qubits that can be afforded by the consumers to (assuming fixed capital available for purchasing),
\begin{align}
	N_\mathrm{tax} = \frac{N_\mathrm{no\,tax}}{\gamma_T}.
\end{align}

@@

This demonstrates that the computational power of classical networks is simply inversely proportional to the rate of taxation, i.e a linear tax performance multiplier, as we intuitively expect. And for quadratic scaling functions the dependence is inverse quadratic in the taxation rate. In both cases the multiplier is a constant factor, independent of the network size. However, for exponential scaling functions we observe an exponential dependence on both the rate of taxation and the size of the network, shown in Fig.~\ref{fig:tax_exp}(left)\comment{Make left or top}. Note that for large networks, executing computations with exponential scaling functions, there is enormous sensitivity to variations in tax rates, yielding very high leverage in computational return by tax rates.

@@

However, taxation could also be negative, in the form of subsidisation. In Fig.~\ref{fig:tax_exp}(right)\comment{Make right or bottom} we focus on the region surrounding neutral taxation, showing small degrees of taxation and subsidisation on either side. Evidently, even small degrees of subsidisation have a very strong impact on the performance multiplier (more pronounced than the same rate of positive taxation!). This makes subsidisation of qubit expansion highly tempting.

@@

An important implication of the imposition of the tax is the share of the taxation burden\index{Taxation}. The change in price from the efficient price, $P_e$, to the new market price faced by consumers, $P_c$, is somewhat equivalent to the shift from $P_e$ to the price point that the suppliers of qubits will receive, $P_s$. This means that the tax burden is likely to be equally shared between producers and consumers, which in the long term could act as a disincentive for increased production.

@@

This will give rise to a marketplace for tradable units of quantum computation, where the underlying asset is time-shares in the global network. We refer to this as the \textit{quantum stock market} -- a marketplace subject to ordinary supply and demand, economic, and of course psychological pressures. In a scenario where a large number of users are executing computations with high return (think the R\&D lab), asset values will be traded up. Contrarily, in a scenario of low-return computations (think our poor undergrad), they will be traded down. These market forces will be highly time-dependent, varying against many other factors in the economy, such as the emergence of new applications for quantum computation -- the discovery of an important new algorithm could spontaneously distort the market leading to major corrections.

@@

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, potentially highly speculative ones, who float their resources on the quantum stock market, betting on changes in demand for computation and their associated subjective cost. This trading could involve transactions in the direct underlying asset, future contracts (Sec.~\ref{sec:for_contr}) for locking in required computational power at future points in time, or more complex derivatives. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates of their licensing. And their return on investment\index{Return on investment (RoI)} will reflect these market dynamics.

As all markets for tradable assets do, sophisticated derivative markets will inevitably emerge, whereby people can speculate on or hedge against market dynamics, taking long, short, or more complex market positions, potentially in a highly-leveraged manner. As discussed in Sec.~\ref{sec:for_contr}, derivatives such as future contracts can be extremely helpful in enabling consumers to lock in future prices, creating a stable and predictable business climate. Similarly, other derivatives will enable market participants to hedge\index{Hedging} other quantum-related investments. For example, suppose an investor held a stake in an R\&D lab, highly reliant on quantum computing resources. By taking a leveraged long position on the market value for computation, he may limit losses on his R\&D investment associated with the higher price (and hence lower profit) they will be paying for computation. No doubt, market manipulation and all the usual nonsense and shenanigans\index{Shenanigans} will ensue.

@@

\captionspacetab \caption{Summary of the dynamics of various economic models under several computational scaling functions ($f_\mathrm{sc}$) of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\mathrm{global}=\sum_{j\in \mathrm{nodes}} n_j$} qubits in the global network. $N_0$ is the initial number of qubits, undergoing growth rate $\gamma_N$. $C_0$ is the initial monetary cost per qubit, undergoing decay rate $\gamma_C$. $\gamma_\mathrm{ror}$ is the rate of return on the licensing of compute-time on qubits, and $r_\mathrm{rf}$ is the risk-free rate of return (typically yield on US government bonds). $\gamma_T$ is the rate of taxation, and $N_\mathrm{tax}$ is the number of qubits that would exist on the network in the absence of taxation.} \label{tab:summary_ec_models}
